---
title: "Main Report"
output: github_document
---
The written report will provide a narrative for your project and present and discuss your findings.
Fourth script: an .Rmd or .ipynb actually, that presents **original data**, **the statistical summaries**, and/or **the figures** in a little report. There should be a written narrative in this document that 
**introduces and justifies your question**, 
**introduces the data set**, 
**presents the findings/results**, 
and **interprets the findings/results** in context of the question. 
**Some critique** of the analysis is also expected (limitations, assumptions, etc) and 
**a statement of future directions** (what would you do next if you had more time to work on this). 
The report is expected to be 1-2 written pages (excluding figures, tables and references). You are expected to have a reference section and cite 2-3 external sources (data source can be one of these citations).





```{r setup, include=FALSE}
library(tidyverse)
library(here)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here())
```

##Airbnb is Amsterdam!

  Airbnb renting has always been interesting. Some spots can be rented in higher prices, whereas other spots can only be rented in very low prices. 
  Suppose you would like to be a host in Amsterdam, in order to be a successful host, it is a good idea to investgate the host listing data from airbnb and see what are the major predictors of the room prices. In this project, we are going to do this job for those who want to be a successful host! Therefore, in our project, a question that is reasonable to ask is: What are the two strongest predictors of price for airbnb listings in Amsterdam? We are going to analyse the host listing data in Amsterdam and find out the answer! 

##Analyzing and Prediction

'minimum_nights','number_of_reviews','calculated_host_listings_count','availability_365'

  From the [Website](http://insideairbnb.com/get-the-data.html), we found the host listing data of Airbnb in Amsterdam. Before starting analyze the data, let's take a look at the data. 

```{r}
data=read_csv("data/listings.csv")
head(data)
```


From the data, we can see that there are several features inside: 

* **id**: Unique identification code for the listing
* **name**: Descriptive name of the listing
* **host_id**: Unique identification code for the host
* **host_name**: First name of the host (privacy is respected. The data is open.)
* **neighbourhood**: A categorical character variable that specifies the name of neighbourhood of the listing
* **latitude**: A numeric variable that combining the **longitude** to represent the location of the listing
* **longtitude**A numeric variable that combining the **latitude** to represent the location of the listing
* **room_type**: A categorical variable including **Shared Room**, **Private Room** or **Entire Room/Apt**.
* **price**: The price of the listing.
* **minimum_nights**: The minimum number of nights the host requires to book their property.
* **number_of_reviews**: Number of customer reviews regarding the listing.
* **last_review**: Date of the last review.
* **reviews_per_month**: Number of customer reviews per month.
* **calculated_host_listings_count**: Number of listings each host has simultaneously.
* **availability_365**: The number of days that the listing is available in a 365 days, which is pre-defined by the host.



  After looking at the data, we predict that `neighbourhood`, `location(latitude and longtitude)`, `room_type`, `minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, and availability_365 can possibly be the factors affecting the price. In order to find out the two strongest predictors, after cleaning the data, we are going to first do data visualzation and have a grasp of these factors visually, then use the decision tree to find out the two strongest predictors. 
  

##Data cleaning
  
  After taking a look of these features, we realized that Neighbourhood and location(latitude and longtitude) could act similarly in affecting the room price, and reviews_per_month and number_of_reviews could act similarly in affecting the room price also. Location is a more complicated feature than Neighbourhood, since it contains two features and we must combine these two features (latitude and longtitude) together when analyzing(otherwise it won't make sense to use them individually). At the moment, we haven't learned how to combine two features into one and implement it in the decision tree. Therefore, at this time, we decide not to use these two features. When we first looked at the data, we believed that reviews_per_month is a better feature to use than number_of_reviews because it is possible that some listing has more reviews because it is on airbnb longer than others. However, when we looked a deep look, we found out that there are more than 2000 missing values in the reviews_per_month, therefore, we decided to use number_of_reviews instead.
  
#However, we found out neighbouhood and room_type are categorical, which can be hard to analyze together with numeric data, so we decide to put them on the shelf at the moment. 
  
#However, we will demostrate how latitude and longtitude affect the price in a map later. Next, we are going to take a closer look to the remining factors, ans implement these features in decision tree: minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, and availability_365. 


##Data Visulazation

  In this section, we are going to analyze if each feature affect the price by visulazing it. 
  The first feature we are going to look at is the 




